Pervasive duplication of tumor suppressor genes preceded parallel evolution

### 2020-05-31 paper_PLOS/paper_PLOS_draft.Rmd
Added Figure, fixed figures 0-5

    ```{r Libraries and functions, include = F}
knitr::opts_chunk$set(eval=T, echo=F, message = F, warning = F, # fig.width=6, 
                      fig.retina = 2, fig.align = "left", dpi = 300, dev="Cairo_pdf")

@@

set.seed(1234)
suppressMessages(suppressWarnings(require(data.table)))
suppressMessages(suppressWarnings(require(tidyverse)))
options(readr.num_columns = 0)
suppressMessages(suppressWarnings(require(ape)))
suppressMessages(suppressWarnings(require(geiger)))
suppressMessages(suppressWarnings(require(nlme)))
suppressMessages(suppressWarnings(require(treeio)))
suppressMessages(suppressWarnings(require(tidytree)))
suppressMessages(suppressWarnings(require(ggtree)))
suppressMessages(suppressWarnings(require(ggimage)))
suppressMessages(suppressWarnings(require(ggpubr)))
suppressMessages(suppressWarnings(require(ggsci)))
suppressMessages(suppressWarnings(require(plotly)))
suppressMessages(suppressWarnings(require(ggplotify)))
suppressMessages(suppressWarnings(require(UpSetR)))
suppressMessages(suppressWarnings(require(ggrepel)))
suppressMessages(suppressWarnings(require(magick)))
suppressMessages(suppressWarnings(require(ggrepel)))
suppressMessages(suppressWarnings(require(gghighlight)))
suppressMessages(suppressWarnings(require(broom.mixed)))
suppressMessages(suppressWarnings(require(purrr)))
suppressMessages(suppressWarnings(require(stargazer)))
source("../code/generalFunctions.R")
```
```{r Data Files, include = F}
UP000005640 <- read_tsv("../data/input/UP000005640.withheader.tsv")
gene_list <- read_lines("../output/recBlastDBPrep/AvA_geneList.txt")
gene_list_filtered <- read_lines("../output/recBlastDBPrep/AvA_geneList_filtered.txt")
genomeTable <- read_csv("../output/other/genomeTable.csv")

@@

t.bodysize.atlantogenata.withNodes <- st.Atlantogenata %>% 
  as_tibble() %>% 
  filter(!is.na(label)) %>%
  select(
    `Node`=label, 
    `Size (log(g))`=Median, 
    `95% CI (Low)` = `95%CI_Low`, 
    `95% CI (High)` = `95%CI_High`,  
    `Rate (sqrt)`=sqrt.rate
  ) %>%
  mutate_at(vars(-`Node`, ), . %>% as.numeric %>% round(2)) %>% 
  knitr::kable(
    ., 
    longtable = TRUE, 
    booktabs = TRUE,
    caption = 'A table generated by the longtable package.'
  )

p.bodysize.atlantogenata <- st.Atlantogenata %>% 
  as_tibble() %>% 
  filter(label %in% st.core) %>% 
  mutate(label = label %>% factor(., levels = c("Loxodontini", "Loxodonta africana","Loxodona", "Loxodonta cyclotis", "Palaeoloxodon antiquus", "Elephantidae", "Elephantina", "Elephas maximus", "Mammuthus", "Mammuthus primigenius", "Mammuthus columbi", "Proboscidea", "Mammut americanum", "Tethytheria", "Trichechus manatus", "Paenungulata", "Procavia capensis", "Pseudoungulata", "Orycteropus afer", "Macroscelidae", "Elephantulus edwardii", "Afrosoricida", "Chrysochloris asiatica", "Echinops telfairi", "Afrotheria", "Xenarthra", "Dasypus novemcinctus", "Choloepus hoffmanni", "Atlantogenata"))) %>% 
  select(-parent, -node, -branch.length) %>%
  ggplot(
    aes(
      y=as.factor(label),
      x=Median, 
      xmin=`95%CI_Low`,
      xmax=`95%CI_High`
      )
  ) +
  geom_pointrange(size=0.5) +
  geom_point(aes(color=Median), size=1) +
  geom_point(aes(x=`95%CI_Low`, color=`95%CI_Low`), size=1.5, stroke=2, pch="[") +
  geom_point(aes(x=`95%CI_High`, color=`95%CI_High`), size=1.5, stroke=2, pch="]") +
  scale_color_viridis_c(limits=c(size.scale.min, size.scale.max), 
                        guide = guide_colorbar(
                          title="Body size (ln(g))",
                          title.theme =  element_text(size = 6, face = "bold", colour = "black"),
                          title.position = "top",
                          title.hjust = 0.5
                          )
                        ) +
  labs(
    x="Body size (95%CI)",
    y="Node"
  ) + 
  theme_pubclean()+
  labs_pubr() + 
  theme(
    text = element_text(face = "plain", 
                        colour = "black", lineheight = 0.9, 
                        hjust = 0.5, vjust = 0.5, angle = 0, margin = margin(), 
                        debug = FALSE), 
    axis.text = element_text(size = 4, 
                               colour = "black", face = "bold"),
    axis.title = element_text(size = 6, 
                              colour = "black", face = "bold"),
    plot.title = element_text(size = 6, 
                              colour = "black", lineheight = 1, face = "bold"), 
    legend.text = element_text(size = 4, 
                               face = "plain", colour = "black"),
    legend.position = "bottom"
  )

@@

```{r Plot Gene Copy Trees, include=F}
p.ml.tree.increasing.geneCounts.withSize <- ml.tree.increasing.geneCounts.withSize %>%
  as_tibble %>% mutate(Spc.short = Spc.short %>% str_c('bold("', ., '")')) %>% 
  as.treedata() %>% 
  ggtree(
    .,
    branch.length = "none",
    #continuous=T,
    aes(
      color=lnSize,
      fill=lnSize
    ),
    size=2
    ) +
  scale_color_viridis_c(guide=F) +
  scale_fill_viridis_c(limits=c(size.scale.min, size.scale.max), guide = guide_colorbar(title="Body size (ln(g))", title.position = "left", title.vjust=1,title.theme = element_text(face="bold"))) +
  geom_tiplab(aes(label=Spc.short), offset = 0.4, color="black", size=4, parse=T)+
  geom_tiplab(aes(label=not.me(lnSize, N.Genes)), geom="label",  offset=-0.5, color="black", size=3)+ 
  geom_tiplab(aes(label=yes.me(lnSize, N.Genes)), geom="label",  offset=-0.5, color="grey", size=3)+ 
  geom_nodelab(aes(x=branch, label=not.me(lnSize, N.Genes)), geom="label", nudge_y = -0.1, nudge_x = -0.5, color="black", size=3)+ 
  geom_nodelab(aes(x=branch, label=yes.me(lnSize, N.Genes)), geom="label", nudge_y = -0.1, nudge_x = -0.5, color="grey", size=3)+ 
  geom_nodelab(aes(x=branch, label=not.me(lnSize, label)), geom="label", nudge_y = 0.5, nudge_x = -0.5, color="black", size=3)+ 
  geom_nodelab(aes(x=branch, label=yes.me(lnSize, label)), geom="label", nudge_y = 0.5, nudge_x = -0.5, color="grey", size=3)+ 
  geom_nodelab2(aes(subset=label=="Root", x=branch), geom="label",
               size=3,
               color="grey")+
  theme_tree() + 
  xlim(0,13) +
  theme(legend.position = "bottom")+
  xlab("Rate of Change, Body Size")
# p.ml.tree.increasing.geneCounts.withSize

@@

)

@@

```{r Fig2 Prep Table 1}
t.cancersucc.atl <- table.cancerSucceptibility.Atlantogenata.genomes %>% 
  # filter(label %in% ml.treedata.table$label) %>%  
  # select(-parent, -node, -branch.length) %>%
  select(
    Node = label, 
    lnSize,
    `Est. Lifespan`=Lifespan,
    `K1` = K1,
    `K2` = K2,
    `Change in K` = CancerSucceptabilityChange,
    `log2 Change` = log2CancerSucceptabilityChange
  ) %>%
  mutate_at(
    vars(`K1`, `K2`, `Change in K`), 
    . %>% formatC(., format = "e", digits = 2)
            ) %>%
  mutate(
    `Est. Lifespan` = `Est. Lifespan` %>% round(2), 
    # `Change in K` = `Change in K` %>% round(2), 
    `log2 Change` = `log2 Change` %>% round(2)
  ) %>% 
  mutate(
    Ancestor = Node %>% 
    sapply(
        .,
        function(n, d=table.cancerSucceptibility.Atlantogenata.genomes){
            p.node <- d %>% filter(label==n) %>% pull(parent) %>% unique
            d %>% filter(node == p.node) %>% pull(label) %>% unique %>% return
        }
    ) %>% str_replace_all("\\.", " ") %>% str_replace("Root", "Atlantogenata") %>% factor(., levels = c("Loxodontini", "Loxodonta africana","Loxodona", "Loxodonta cyclotis", "Palaeoloxodon antiquus", "Elephantidae", "Elephantina", "Elephas maximus", "Mammuthus", "Mammuthus primigenius", "Mammuthus columbi", "Proboscidea", "Mammut americanum", "Tethytheria", "Trichechus manatus", "Paenungulata", "Procavia capensis", "Pseudoungulata", "Orycteropus afer", "Macroscelidae", "Elephantulus edwardii", "Afrosoricida", "Chrysochloris asiatica", "Echinops telfairi", "Afrotheria", "Xenarthra", "Dasypus novemcinctus", "Choloepus hoffmanni", "Atlantogenata", "Afroinsectivora")),
        Node = Node %>% str_replace_all("\\.", " ") %>% factor(., levels = c("Loxodontini", "Loxodonta africana","Loxodona", "Loxodonta cyclotis", "Palaeoloxodon antiquus", "Elephantidae", "Elephantina", "Elephas maximus", "Mammuthus", "Mammuthus primigenius", "Mammuthus columbi", "Proboscidea", "Mammut americanum", "Tethytheria", "Trichechus manatus", "Paenungulata", "Procavia capensis", "Pseudoungulata", "Orycteropus afer", "Macroscelidae", "Elephantulus edwardii", "Afrosoricida", "Chrysochloris asiatica", "Echinops telfairi", "Afrotheria", "Xenarthra", "Dasypus novemcinctus", "Choloepus hoffmanni", "Atlantogenata", "Afroinsectivora"))
  ) %>%
    arrange(Node) %>% 
  select(Node, `Est. Lifespan`, K1, K2, `Change in K`, `log2 Change`) %>% 
  knitr::kable(
    ., 
    longtable = TRUE, 
    booktabs = TRUE,
    caption = 'Estimated Cancer Succeptibilty for nodes in Atlantogenata'
  )
```
```{r Figure2, fig.cap="Cancer succecptibility across Atlantogenata", out.width="6in", fig.asp=1}
f2
```

@@

p.cor.GCT.CEGMA <-
  cor.GCT.CEGMA %>%
  ggplot(
    aes(x=Var1, y=Var2, fill = value)
  )+
  geom_tile(color = "white")+
  theme_minimal()+
  coord_fixed()+
  scale_x_discrete(
    position = "top"
    ) +
  scale_y_discrete(position = "right") +
  scale_fill_viridis_c(breaks = c(-1,-0.5, 0, 0.5, 1),labels = c(-1,-0.5, 0, 0.5, 1)) +
  theme(
    axis.text.x = element_text(
      angle = -330, vjust = 0,
      size = highlightTextSize(cor.GCT.CEGMA$Var1, cor.toHighlight, sizes = c(6,9)), 
      color = highlightTextColor(cor.GCT.CEGMA$Var1, cor.toHighlight, color = c("black", "red")), 
      hjust = 0
    ),
    axis.text.y = element_text(
      size = highlightTextSize(cor.GCT.CEGMA$Var2, cor.toHighlight, sizes = c(6,9)), 
      color = highlightTextColor(cor.GCT.CEGMA$Var2, cor.toHighlight, color = c("black", "red"))
    ),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.ticks = element_blank(),
    legend.justification = c(1, 1),
    legend.position = c(0.4,0.7), #c(0.6, 0.7),
    legend.direction = "horizontal",
    legend.text = element_text(size=9),
    legend.title =  element_text(size=11)
    ) +
  guides(
    fill = guide_colorbar(
      title="Pearson\nCorrelation",
      barwidth = 7, barheight = 1,
      title.position = "top", title.hjust = 0.5,
      draw.llim = T
    )
  )
```
```{r Phylogenetic Correlations}

@@

# #clades
# genome.table.forFig[str_detect(genome.table.forFig$`Common Name`, "Elephant$|Mammoth$"),]$Clade <- "Paenungulata, Probodiscea"
# genome.table.forFig[str_detect(genome.table.forFig$`Common Name`, "Mastodon"),]$Clade <- "Paenungulata, Probodiscea"
# genome.table.forFig[str_detect(genome.table.forFig$`Common Name`, "^Cape|Tenrec"),]$Clade <- "Macroscelididae/Afroinsectivora"
# genome.table.forFig[str_detect(genome.table.forFig$`Common Name`, "Manatee"),]$Clade <- "Paenungulata, Tethytheria"
# genome.table.forFig[str_detect(genome.table.forFig$`Common Name`, "Hyrax"),]$Clade <- "Paenungulata"
# genome.table.forFig[str_detect(genome.table.forFig$`Common Name`, "Aardvark"),]$Clade <- "Pseudoungulata"
# genome.table.forFig[str_detect(genome.table.forFig$`Common Name`, "Sloth|Armadillo"),]$Clade <- "Xenarthra"
# 
# #Lifespan caveats
# genome.table.forFig[which(genome.table.forFig$Species == "Elephantulus edwardii"),]$`Lifespan (y)` = "~5.7*"
# genome.table.forFig[which(genome.table.forFig$Species == "Loxodonta cyclotis"),]$`Lifespan (y)` = paste0(genome.table.forFig[which(genome.table.forFig$Species == "Loxodonta africana"),]$`Lifespan (y)`, "\u2020")
```
```{r Figure3 Prep Genome Table}
ggt.GenomeTable.withNote <- genome.table.forFig %>% 
  select(Species, `Common Name`, starts_with("Size"), starts_with("#"), starts_with("%"), starts_with("Mean")) %>% 
  arrange(Species)%>% 
  knitr::kable(
    ., 
    longtable = TRUE, 
    booktabs = TRUE,
    caption = 'Summary of duplications in Atlantogenata'
  )
```
```{r Table2, fig.height=8, fig.width=6}
ggt.GenomeTable.withNote
```

```{r Figure3, fig.cap="Gene duplications occur readily throughout Atlantogenata. A) A table summarizing duplication events in Atlantogenata. B) A tree of the species in Atlantogenata with genomes, with the number of genes that underwent an increase in copy number overlayed at each node.", fig.height=8, fig.width=6}

@@

```{r Figure4, fig.cap="Correlations between genome quality metrics and ECNC metrics"}
f4 <- p.cor.GCT.CEGMA
f4
```

@@

p.ORA <- ORA.numbers.ReactomeOnly %>% 
  filter(Direction == "increased") %>% 
  select(-Direction) %>% 
  knitr::kable(
    ., 
    longtable = TRUE, 
    booktabs = TRUE,
    caption = 'Number of pathways overrepresented among duplicated genes at different FDRs.'
  )

>>>>

    ```{r Libraries and functions, include = F}
knitr::opts_chunk$set(eval=T, echo=F, message = F, warning = F, # fig.width=6, 
                      fig.retina = 2, fig.align = "left", dpi = 300)

@@

set.seed(1234)
suppressMessages(suppressWarnings(require(data.table)))
suppressMessages(suppressWarnings(require(tidyverse)))
options(readr.num_columns = 0)
suppressMessages(suppressWarnings(require(ape)))
suppressMessages(suppressWarnings(require(geiger)))
suppressMessages(suppressWarnings(require(nlme)))
suppressMessages(suppressWarnings(require(treeio)))
suppressMessages(suppressWarnings(require(tidytree)))
suppressMessages(suppressWarnings(require(ggtree)))
suppressMessages(suppressWarnings(require(ggimage)))
suppressMessages(suppressWarnings(require(ggpubr)))
suppressMessages(suppressWarnings(require(ggsci)))
suppressMessages(suppressWarnings(require(plotly)))
suppressMessages(suppressWarnings(require(ggplotify)))
suppressMessages(suppressWarnings(require(UpSetR)))
suppressMessages(suppressWarnings(require(ggrepel)))
suppressMessages(suppressWarnings(require(magick)))
suppressMessages(suppressWarnings(require(ggrepel)))
suppressMessages(suppressWarnings(require(gghighlight)))
suppressMessages(suppressWarnings(require(broom.mixed)))
suppressMessages(suppressWarnings(require(purrr)))
suppressMessages(suppressWarnings(require(kableExtra)))
suppressMessages(suppressWarnings(require(stargazer)))
source("../code/generalFunctions.R")
```
```{r Data Files, include = F}
UP000005640 <- read_tsv("../data/input/UP000005640.withheader.tsv")
gene_list <- read_lines("../output/recBlastDBPrep/AvA_geneList.txt")
gene_list_filtered <- read_lines("../output/recBlastDBPrep/AvA_geneList_filtered.txt")
genomeTable <- read_csv("../output/other/genomeTable.csv")

@@

t.bodysize.atlantogenata.withNodes <- st.Atlantogenata %>% 
  as_tibble() %>% 
  filter(!is.na(label)) %>%
  select(
    `Node`=label, 
    `Size (log(g))`=Median, 
    `95% CI (Low)` = `95%CI_Low`, 
    `95% CI (High)` = `95%CI_High`,  
    `Rate (sqrt)`=sqrt.rate
  ) %>%
  mutate_at(vars(-`Node`, ), . %>% as.numeric %>% round(2)) %>% 
  kable(
    ., 
    longtable = TRUE, 
    booktabs = TRUE,
    caption = 'All body size estimates for _Atlantogenata_.'
  )

p.bodysize.atlantogenata <- st.Atlantogenata %>% 
  as_tibble() %>% 
  filter(label %in% st.core) %>% 
  mutate(label = label %>% factor(., levels = c("Loxodontini", "Loxodonta africana","Loxodona", "Loxodonta cyclotis", "Palaeoloxodon antiquus", "Elephantidae", "Elephantina", "Elephas maximus", "Mammuthus", "Mammuthus primigenius", "Mammuthus columbi", "Proboscidea", "Mammut americanum", "Tethytheria", "Trichechus manatus", "Paenungulata", "Procavia capensis", "Pseudoungulata", "Orycteropus afer", "Macroscelidae", "Elephantulus edwardii", "Afrosoricida", "Chrysochloris asiatica", "Echinops telfairi", "Afrotheria", "Xenarthra", "Dasypus novemcinctus", "Choloepus hoffmanni", "Atlantogenata"))) %>% 
  select(-parent, -node, -branch.length) %>%
  ggplot(
    aes(
      y=as.factor(label),
      x=Median, 
      xmin=`95%CI_Low`,
      xmax=`95%CI_High`
      )
  ) +
  geom_pointrange(size=0.5) +
  geom_point(aes(color=Median), size=1) +
  geom_point(aes(x=`95%CI_Low`, color=`95%CI_Low`), size=1.5, stroke=2, pch="[") +
  geom_point(aes(x=`95%CI_High`, color=`95%CI_High`), size=1.5, stroke=2, pch="]") +
  scale_color_viridis_c(limits=c(size.scale.min, size.scale.max), 
                        guide = guide_colorbar(
                          title="Body size (ln(g))",
                          title.theme =  element_text(size = 6, face = "bold", colour = "black"),
                          title.position = "top",
                          title.hjust = 0.5
                          )
                        ) +
  labs(
    x="Body size (95%CI)",
    y="Node"
  ) + 
  theme_pubclean()+
  labs_pubr() + 
  theme(
    text = element_text(face = "plain", 
                        colour = "black", lineheight = 0.9, 
                        hjust = 0.5, vjust = 0.5, angle = 0, margin = margin(), 
                        debug = FALSE), 
    axis.text = element_text(size = 6, 
                               colour = "black", face = "bold"),
    axis.title = element_text(size = 8, 
                              colour = "black", face = "bold"),
    plot.title = element_text(size = 8, 
                              colour = "black", lineheight = 1, face = "bold"), 
    legend.text = element_text(size = 6, 
                               face = "plain", colour = "black"),
    legend.position = "bottom"
  )

@@

```{r Plot Gene Copy Trees, include=F}
p.ml.tree.increasing.geneCounts.withSize <- ml.tree.increasing.geneCounts.withSize %>%
  as_tibble %>% mutate(Spc.short = Spc.short %>% str_c('bold("', ., '")')) %>% 
  as.treedata() %>% 
  ggtree(
    .,
    branch.length = "none",
    #continuous=T,
    aes(
      color=lnSize,
      fill=lnSize
    ),
    size=2
    ) +
  scale_color_viridis_c(guide=F) +
  scale_fill_viridis_c(limits=c(size.scale.min, size.scale.max), guide = guide_colorbar(title="Body size (ln(g))", title.position = "left", title.vjust=1,title.theme = element_text(face="bold"))) +
  geom_tiplab(aes(label=Spc.short), offset = 0.4, color="black", size=4, parse=T)+
  geom_tiplab(aes(label=not.me(lnSize, N.Genes, threshold = 7)), geom="label",  offset=-0.5, color="black", size=2, fontface="bold")+ 
  geom_tiplab(aes(label=yes.me(lnSize, N.Genes, threshold = 7)), geom="label",  offset=-0.5, color="grey", size=2)+ 
  geom_nodelab(aes(x=branch, label=not.me(lnSize, N.Genes, threshold = 7)), geom="label", nudge_y = -0.1, nudge_x = -0.5, color="black", size=2, fontface="bold")+ 
  geom_nodelab(aes(x=branch, label=yes.me(lnSize, N.Genes, threshold = 7)), geom="label", nudge_y = -0.1, nudge_x = -0.5, color="grey", size=2, fontface="bold")+ 
  geom_nodelab(aes(x=branch, label=not.me(lnSize, label, threshold = 7)), geom="label", nudge_y = 0.5, nudge_x = -0.5, color="black", size=2, fontface="bold")+ 
  geom_nodelab(aes(x=branch, label=yes.me(lnSize, label, threshold = 7)), geom="label", nudge_y = 0.5, nudge_x = -0.5, color="grey", size=2, fontface="bold")+ 
  geom_nodelab2(aes(subset=(label=="Root"), label = "Atlantogenata", x=branch), geom="label",
               size=2,
               color="grey")+
  theme_tree() + 
  xlim(-0.5,13) +
  xlab("Rate of Change, Body Size") + 
  theme(
    legend.position="bottom",
    # panel.background = element_rect(fill = "lightgrey"),
    text = element_text(face = "plain", 
                        colour = "black", lineheight = 0.9, 
                        hjust = 0.5, vjust = 0.5, angle = 0, margin = margin(), 
                        debug = FALSE), 
    axis.text.x = element_text(size = 4, 
                               colour = "black", face = "bold"),
    axis.title = element_text(size = 6, 
                              colour = "black", face = "bold"),
    plot.title = element_text(size = 6, 
                              colour = "black", lineheight = 1, face = "bold"), 
    legend.title = element_text(size = 6, 
                                face = "bold", colour = "black"), 
    legend.text = element_text(size = 6, 
                               face = "plain", colour = "black")
  )
# p.ml.tree.increasing.geneCounts.withSize

@@

```{r Figure0Prep}

groups.atlantogenata <- list(
  # "Atlantogenata",
  "Elephantidae" = c("Loxodonta.africana", "Loxodonta.cyclotis", "Palaeoloxodon.antiquus", "Elephas.maximus", "Mammuthus.columbi", "Mammuthus.primigenius"),
  "Proboscidea" = c("Mammut.americanum"),
  "Tethytheria" = c("Trichechus.manatus"),
  "Paenungulata" = c("Procavia.capensis"),
  "Pseudoungulata" = c("Orycteropus.afer"),
  "Xenarthra" = c("Dasypus.novemcinctus", "Choloepus.hoffmanni"),
  "Afrosoricida" = c("Chrysochloris.asiatica"), 
  "Macroscelidea" = c("Elephantulus.edwardii", "Echinops.telfairi")
)

anage.genomeSpecies <- anage %>% filter(label %in% genomeTable.atlantogenata$label)
anage.genomeSpecies <- anage.genomeSpecies %>% select(label, Lifespan) %>% 
  full_join(tree.Atlantogenata.table %>% filter(label %in% genomeTable.atlantogenata$label) %>% select(label, Size=Median, phyloPicUID), by = "label")

label.phylopic <- anage.genomeSpecies %>% select(label, uid=phyloPicUID)

time.tree.atlantogenata.genomeSpecies <- time.tree.atlantogenata %>% 
  drop.tip(time.tree.atlantogenata$tip.label[!time.tree.atlantogenata$tip.label %in% genomeTable.atlantogenata$label]) %>% 
  full_join(label.phylopic, by="label") %>% 
  as_tibble %>%
  mutate(prettyLabel = label %>% str_replace("\\.", "\n")) %>% 
  groupOTU(groups.atlantogenata) %>% #print(n=12412)
  as.treedata()

atlantogenata.tree.size.lifespan <-
time.tree.atlantogenata.genomeSpecies %>% 
  ggtree() %>% 
  flip(tree_view = ., node1 =nodeid(time.tree.atlantogenata.genomeSpecies, "Loxodonta.africana"), node2 = MRCA(time.tree.atlantogenata.genomeSpecies, "Palaeoloxodon.antiquus", "Loxodonta.cyclotis")) %>% 
  revts() +
  geom_tiplab(aes(image=uid, size=I(0.1), color = group), geom = "phylopic") +
  geom_tiplab(aes(label=prettyLabel), size=3, offset = 20) +
  xlab("Divergence time (MYA)") +
  geom_facet(
    data = anage.genomeSpecies,
    panel = "ln(Size)",
    mapping = aes(x=Size),
    geom = ggstance::geom_barh,
    stat = "identity", 
    fill = "aquamarine"
  ) + 
  geom_facet(
    data = anage.genomeSpecies,
    panel = "Lifespan",
    mapping = aes(x=Lifespan),
    geom = ggstance::geom_barh,
    stat = "identity",
    fill = "goldenrod"
  ) + 
  theme_tree2() +
  xlim_tree(c(-90, 65)) + 
  theme(
    legend.position="bottom",
    # panel.background = element_rect(fill = "lightgrey"),
    text = element_text(face = "plain", 
                        colour = "black", lineheight = 0.9, 
                        hjust = 0.5, vjust = 0.5, angle = 0, margin = margin(), 
                        debug = FALSE), 
    axis.text.x = element_text(size = 4, 
                               colour = "black", face = "bold"),
    axis.title = element_text(size = 6, 
                              colour = "black", face = "bold"),
    plot.title = element_text(size = 6, 
                              colour = "black", lineheight = 1, face = "bold"), 
    legend.title = element_text(size = 8, 
                                face = "bold", colour = "black"), 
    legend.text = element_text(size = 6, 
                               face = "plain", colour = "black"),
    strip.text.y = element_text(size=8, face="bold")
  )  + 
  guides(color=guide_legend(title="Clade", title.position = "left"))

atlantogenata.tree.size.lifespan %<>% facet_widths(c(2,1,1))

```
```{r Figure0, fig.cap="Atlantogenatans with sequenced genomes, body sizes, and known lifespans [@PuttickAndThomas2015; @HAGR]",  out.width="6in", fig.asp=1.3}
atlantogenata.tree.size.lifespan
```

@@

```{r Fig2 Prep Table 1}
t.cancersucc.atl <- table.cancerSucceptibility.Atlantogenata.genomes %>% 
  # filter(label %in% ml.treedata.table$label) %>%  
  # select(-parent, -node, -branch.length) %>%
  select(
    Node = label, 
    lnSize,
    `Est. Lifespan`=Lifespan,
    `K1` = K1,
    `K2` = K2,
    `Change in K` = CancerSucceptabilityChange,
    `log2 Change` = log2CancerSucceptabilityChange
  ) %>%
  mutate_at(
    vars(`K1`, `K2`, `Change in K`), 
    . %>% formatC(., format = "e", digits = 2)
            ) %>%
  mutate(
    `Est. Lifespan` = `Est. Lifespan` %>% round(2), 
    # `Change in K` = `Change in K` %>% round(2), 
    `log2 Change` = `log2 Change` %>% round(2)
  ) %>% 
  mutate(
    Ancestor = Node %>% 
    sapply(
        .,
        function(n, d=table.cancerSucceptibility.Atlantogenata.genomes){
            p.node <- d %>% filter(label==n) %>% pull(parent) %>% unique
            d %>% filter(node == p.node) %>% pull(label) %>% unique %>% return
        }
    ) %>% str_replace_all("\\.", " ") %>% str_replace("Root", "Atlantogenata") %>% factor(., levels = c("Loxodontini", "Loxodonta africana","Loxodona", "Loxodonta cyclotis", "Palaeoloxodon antiquus", "Elephantidae", "Elephantina", "Elephas maximus", "Mammuthus", "Mammuthus primigenius", "Mammuthus columbi", "Proboscidea", "Mammut americanum", "Tethytheria", "Trichechus manatus", "Paenungulata", "Procavia capensis", "Pseudoungulata", "Orycteropus afer", "Macroscelidae", "Elephantulus edwardii", "Afrosoricida", "Chrysochloris asiatica", "Echinops telfairi", "Afrotheria", "Xenarthra", "Dasypus novemcinctus", "Choloepus hoffmanni", "Atlantogenata", "Afroinsectivora")),
        Node = Node %>% str_replace_all("\\.", " ") %>% factor(., levels = c("Loxodontini", "Loxodonta africana","Loxodona", "Loxodonta cyclotis", "Palaeoloxodon antiquus", "Elephantidae", "Elephantina", "Elephas maximus", "Mammuthus", "Mammuthus primigenius", "Mammuthus columbi", "Proboscidea", "Mammut americanum", "Tethytheria", "Trichechus manatus", "Paenungulata", "Procavia capensis", "Pseudoungulata", "Orycteropus afer", "Macroscelidae", "Elephantulus edwardii", "Afrosoricida", "Chrysochloris asiatica", "Echinops telfairi", "Afrotheria", "Xenarthra", "Dasypus novemcinctus", "Choloepus hoffmanni", "Atlantogenata", "Afroinsectivora"))
  ) %>%
    arrange(Node) %>% 
  select(Node, `Est. Lifespan`, K1, K2, `Change in K`, `log2 Change`) %>% 
  kable(
    ., 
    booktabs = TRUE,
    caption = 'Estimated Cancer Succeptibilty for nodes in Atlantogenata'
  ) %>% 
  kable_styling(latex_options = c("scale_down"))
```
```{r Figure2, fig.cap="Cancer succecptibility across Atlantogenata", out.width="6in", fig.asp=1}
f2
```

@@

  # theme_pubclean()+
  # labs_pubr() + 
  # theme(
  #   text = element_text(face = "plain", 
  #                       colour = "black", lineheight = 0.9, 
  #                       hjust = 0.5, vjust = 0.5, angle = 0, margin = margin(), 
  #                       debug = FALSE), 
  #   axis.text = element_text(size = 6, 
  #                              colour = "black", face = "bold"),
  #   axis.title = element_text(size = 8, 
  #                             colour = "black", face = "bold"),
  #   plot.title = element_text(size = 8, 
  #                             colour = "black", lineheight = 1, face = "bold"), 
  #   legend.text = element_text(size = 6, 
  #                              face = "plain", colour = "black"),
  #   legend.position = "bottom"
  # )
p.cor.GCT.CEGMA <-
  cor.GCT.CEGMA %>%
  ggplot(
    aes(x=Var1, y=Var2, fill = value)
  )+
  geom_tile(color = "white")+
  theme_minimal()+
  coord_fixed()+
  scale_x_discrete(
    position = "top"
  ) +
  scale_y_discrete(position = "right") +
  scale_fill_viridis_c(breaks = c(-1,-0.5, 0, 0.5, 1),labels = c(-1,-0.5, 0, 0.5, 1)) +
  theme_pubclean() +
  theme(
    axis.text.x = element_text(
      angle = -330, vjust = 0,
      size = highlightTextSize(cor.GCT.CEGMA$Var1, cor.toHighlight, sizes = c(6,9)), 
      color = highlightTextColor(cor.GCT.CEGMA$Var1, cor.toHighlight, color = c("black", "red")), 
      hjust = 0
    ),
    axis.text.y = element_text(
      size = highlightTextSize(cor.GCT.CEGMA$Var2, cor.toHighlight, sizes = c(6,9)), 
      color = highlightTextColor(cor.GCT.CEGMA$Var2, cor.toHighlight, color = c("black", "red"))
    ),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.ticks = element_blank(),
    legend.justification = c(1, 1),
    legend.position = c(0.4,0.7), #c(0.6, 0.7),
    legend.direction = "horizontal",
    legend.text = element_text(size=9),
    legend.title =  element_text(size=11)
  ) +
  guides(
    fill = guide_colorbar(
      title="Pearson\nCorrelation",
      barwidth = 7, barheight = 1,
      title.position = "top", title.hjust = 0.5,
      draw.llim = T
    )
  )
```
```{r Phylogenetic Correlations}

@@

# #clades
# genome.table.forFig[str_detect(genome.table.forFig$`Common Name`, "Elephant$|Mammoth$"),]$Clade <- "Paenungulata, Probodiscea"
# genome.table.forFig[str_detect(genome.table.forFig$`Common Name`, "Mastodon"),]$Clade <- "Paenungulata, Probodiscea"
# genome.table.forFig[str_detect(genome.table.forFig$`Common Name`, "^Cape|Tenrec"),]$Clade <- "Macroscelididae/Afroinsectivora"
# genome.table.forFig[str_detect(genome.table.forFig$`Common Name`, "Manatee"),]$Clade <- "Paenungulata, Tethytheria"
# genome.table.forFig[str_detect(genome.table.forFig$`Common Name`, "Hyrax"),]$Clade <- "Paenungulata"
# genome.table.forFig[str_detect(genome.table.forFig$`Common Name`, "Aardvark"),]$Clade <- "Pseudoungulata"
# genome.table.forFig[str_detect(genome.table.forFig$`Common Name`, "Sloth|Armadillo"),]$Clade <- "Xenarthra"
# 
# #Lifespan caveats
# genome.table.forFig[which(genome.table.forFig$Species == "Elephantulus edwardii"),]$`Lifespan (y)` = "~5.7*"
# genome.table.forFig[which(genome.table.forFig$Species == "Loxodonta cyclotis"),]$`Lifespan (y)` = paste0(genome.table.forFig[which(genome.table.forFig$Species == "Loxodonta africana"),]$`Lifespan (y)`, "\u2020")
```
```{r Figure3 Prep Genome Table}
ggt.GenomeTable.withNote <- genome.table.forFig %>% 
  select(Species, `Common Name`, starts_with("Size"), starts_with("#"), starts_with("%"), starts_with("Mean")) %>% 
  arrange(Species)%>% 
  kable(
    ., 
    booktabs = TRUE,
    caption = 'Summary of duplications in Atlantogenata'
  ) %>% 
  kable_styling(latex_options = c("scale_down"))
```
```{r Table2, fig.height=8, fig.width=6}
ggt.GenomeTable.withNote
```

```{r Figure3, fig.cap="Gene duplications occur readily throughout Atlantogenata. A) A table summarizing duplication events in Atlantogenata. B) A tree of the species in Atlantogenata with genomes, with the number of genes that underwent an increase in copy number overlayed at each node.", out.height="7in", out.width="6in"}

@@

```{r Figure4, fig.cap="Correlations between genome quality metrics and ECNC metrics", fig.asp=1, out.width="5in", out.height="5in", fig.align="center"}
f4 <- p.cor.GCT.CEGMA
f4
```

@@

p.ORA <- ORA.numbers.ReactomeOnly %>% 
  filter(Direction == "increased") %>% 
  select(-Direction) %>% 
  mutate(Node = Node %>% str_replace_all("_", " ")) %>% 
  kable(
    ., 
    booktabs = TRUE,
    caption = 'Number of pathways overrepresented among duplicated genes at different FDRs.'
  ) %>% 
  kable_styling(latex_options = c("scale_down"))  # TODO: Make "Number of Pathways" a group, and make each column just "FDR<=XX"
